
\documentclass[ms.tex]{subfiles}
\begin{document}

\section{Conclusions}
\label{sec:conclusions}

We have started from first principles with poisson sampling from an arbitrary
evolutionary track in abundance space.
From this, we derive a likelihood function for fitting one-zone GCE models to
observed stellar abundances and ages, where available (see equation
\ref{eq:likelihood} in~\S~\ref{sec:fitting} and derivation in
Appendix~\ref{sec:likelihood}).
This derivation does not assume that the observational benchmarks are
stellar ages and abundances, and it should therefore be easily extensible to
other astrophysical models in which the chief prediction is a track of some
form (e.g. stellar streams in kinematic space and isochrones in CMDs).
Although there are a handful of examples in the literature already in which
the authors derive best-fit parameters for GCE models~\citep[e.g.][]{Kirby2011,
Spitoni2020, Spitoni2021, Hasselquist2021}, to our knowledge this is the first
of such instances in which the statistical validity of the method has been
robustly demonstrated.
\par
There are two central features to our likelihood function which appear in all
of its forms.
First, the likelihood of observing some datum~$\script{D}_i$ must be
marginalized over the entire evolutionary track~\script{M}.
This requirement arises due to observational uncertainties: for any given
datum, there is no way of knowing where on the track the observation truly
arose from, and to properly take this into account, one must consider all
pair-wise combinations of~\script{D}~and~\script{M}.
Second, the likelihood of observing a datum~$\script{D}_i$ given a point on
the evolutionary track~$\script{M}_j$ must be weighted by the SFR at that time
in the model, simultaneously folding in any selection effects introduced by the
survey.
This requirement arises because an observed star is proportionally more likely
to have been sampled from an epoch of a galaxy's history in which the SFR was
large and/or if the survey designed is biased toward certain epochs.
\par
We establish the accuracy of this fitting method by means of mock data samples.
To this end, we sample from the SFH of an input one-zone model and perturb the
ages and abundances by some artificial uncertainty.
Within the range of sample sizes ($N = 20 - 2000$), abundance uncertainties
($\sigma_\text{[X/Y]} = 0.01 - 0.5$), age uncertainties
($\sigma_{\log_{10}(\text{age})} = 0.02 - 1$) and the fraction of the sample
with age information ($f_\text{age} = 0 - 1$) probed here, we find that this
method recovers the known evolutionary parameters of the input model in all
cases (see Fig.~\ref{fig:accuracy}).
The mean offset between the known and best-fit values is at the~$\sim 1 \sigma$
level, exactly as expected for a Gaussian random process (see discussion
in~\S~\ref{sec:mocks:variations}).
We have conducted further ``stress tests'' of this method by fitting models
with complicated evolutionary histories whichwe elect not to illustrate in this
paper.
In all cases, our method accurately recovers the input model parameters,
reinforicng our interpretation that equation~\refp{eq:likelihood} should be
universally applicable to GCE models as it takes the model-predicted track as
input and is independent of the details of the model from which it was
computed.
We emphasize that it is not that the marginalization over the track and the
weights each individually improve the precision of the fit; it is that they
are both~\textit{essential} to the accuracy of the inferred parameters.
When either of the two are neglected from our fitting procedure, we fail to
recover the known parameters with discrepancies at the many-$\sigma$ level.
\par
Interestingly, our likelihood function accurately recovers input timescales
even in the~\textit{absence} of age information, including the total duration
of star formation.
This arises through their impact on the centroid and shape of the MDF,
information which can be extracted with a fit to a sample of sufficient size
and measurement precision.
While age information does improve the precision of the fit, the inferred
values remain accurate nonetheless even without such measurements.
However, we find significant differences in the inferred evolutionary
timescales when fitting our GSE sample with and without ages.
This discrepancy suggests that in application to observed data, this requires
removing all systematic differences between the data and model and that age
information provides more information than our theoretical justification would
suggest.
Nonetheless, this method could be of notable use to authors interested in
deriving quenching times for dwarf galaxies (i.e. the lookback time to when
star formation stopped).
At present, the most robust method for empirically measuring a galaxy's
quenching time is to directly measure its SFH by some means, such as analysing
its CMD~\citep[e.g.][]{Sohn2013, Weisz2015}.
At present, this leaves only a handful of galaxies with well-constrained SFHs
outside of the Milky Way subgroup~\citep{Monelli2010a, Monelli2010b,
Weisz2014a}.
By constraining the quenching times and SFHs from stellar abundances and ages
(or, alternatively, some empirically-motivated prior on the SFH), these
chemically-derived evolutionary histories could offer new and independent
insight into galaxy formation at the low stellar mass regime.
\par
We apply our fitting method to the GSE~\citep{Belokurov2018, Helmi2018} and
Wukong~\citep{Naidu2020, Naidu2022} stellar streams in the Milky Way halo using
data from the H3 survey~\citep{Conroy2019}.
We find that the Wukong progenitor experienced a more extended infall history
than GSE ($\tau_\text{in} = 3.46^{+3.58}_{-1.36}$ Gyr versus
$\tau_\text{in} = 1.01 \pm 0.13$ Gyr) but that its duration of star formation
was~$\sim$2 Gyr shorter.
The Wukong stream also experienced~$\sim$5 times stronger winds and~$\sim$3
times less efficient star formation than the GSE.
These results point to the Wukong progenitor being significantly lower stellar
mass than the GSE progenitor, an unsurprising result since the GSE is believed
to be among the most massive satellites to have been accreted by the Milky Way
\citep{Myeong2018, Deason2019, Fattahi2019, Mackereth2019, Vincenzo2019}.
Such an interpretation is also in qualitative agreement with semi-analytic
models of galaxy formation, which suggest that dwarf galaxies in the field
experience more extended SFHs~\citep{Baugh2006, Somerville2015a, Behroozi2019}.
The parametrization of our GCE models is however independent of stellar mass,
so they offer no constraints the normalization of the SFH.
\par
Although these models are statistically good descriptions of our GSE and Wukong
data, they are simplified in nature.
For example, we have assumed a linear relation between the gas supply and the
star formation rate while observational results would suggest a non-linear
relation~\citep[e.g.][]{Kennicutt1998, Kennicutt2012, delosReyes2019,
Kennicutt2021}.
The primary motivation of this paper is to provide proof of concept for this
fitting method with an example application to observations consistent with
simple evolutionary histories.
We reserve more careful modelling of galaxies with complex evolutionary
histories for future work.
\par
The methods outlined in this paper are only as accurate as the instantaneous
mixing approximation on a galaxy-by-galaxy basis, which likely limits the
most reliable application to the dwarf galaxy regime (see discussion
in~\S~\ref{sec:onezone}).
In larger galaxies such as the Milky Way, processes such as radial gas flows
\citep[e.g.][]{Lacey1985, Bilitewski2012} and the radial migration of stars
\citep[e.g.][]{Sellwood2002, Loebman2011, Okalidis2022} are expected to
significantly impact the observed abundance distributions in a given Galactic
region.
These results have prompted the development of a number of so-called
``multi-zone'' GCE models~\citep[e.g.][]{Schoenrich2009, Johnson2021, Chen2022}
which stitch together multiple one-zone models via the exchange of gas and
stars.
Though we do not consider these models here, it is an interesting potential
direction for future work to properly compute statistical likelihood in the
presence of multiple evolutionary tracks.
Such models could provide valuable insight into the evolution of higher mass
galaxies with data from next-generation spectroscopic surveys like Milky
Way Mapper~\citep{Kollmeier2017}.
As increasingly sensitive instruments come online, statistically robust methods
such as this will be essential to extract the lessons that can be learned
about galaxies of all stellar masses.

\end{document}

































